Data Migration under a Changing Schema

### 2023-07-13 2022Migration/articleMigrationFACS.tex
Made the definition of Event more readable.

\begin{definition}[Event]
   Let $R \subseteq \Rels$ and $I \subseteq \Rels$ be sets of relations, and let $\infsys=\pair{\schema}{\dataset}$ and  $\infsys'=\pair{\schema}{\dataset'}$ be information systems, and:
      \begin{align}
      \triples_{\dataset} - (\Triple{\Atoms}{(R \cup I)}{\Atoms}) &= \triples_{\dataset'} - (\Triple{\Atoms}{(R \cup I)}{\Atoms})
   \label{eqn:eventUnchanged}\\
      \triples_{\dataset} - (\Triple{\Atoms}{R}{\Atoms}) &\subseteq \triples_{\dataset'} - (\Triple{\Atoms}{R}{\Atoms})
   \label{eqn:eventInsert}
   \end{align}
%   Then we say that $\pair{\pair{\schema}{\dataset}}{\infsys'}$ is an event with scope $R$ inserting in $I$.
   Then we say that $\infsys\xrightarrow[I]{R} \infsys'$ is an event
   that brings the system $\infsys$ to $\infsys'$ inserting pairs in relations from $I$ and updating (i.e. deleting and inserting) pairs in $R$.
%   We use the notation $\pair{\schema}{\dataset} \xrightarrow[I]{R} \infsys'$ to indicate this.
\end{definition}

   equation~\ref{eqn:eventUnchanged} states that the triples of those for relations in $I$ or $R$ are the only ones to have changed, and equation~\ref{eqn:eventInsert} states that of the ones that are only in $I$, no triples were removed.
   %If $I$ or $R$ is the empty set, we omit it from the arrow, so $\infsys \xrightarrow{R} \infsys'$ is a notation for $\infsys \xrightarrow[\emptyset]{R} \infsys'$.

>>>>

\begin{definition}[Event]
   Let $R \subseteq \Rels$ and $I \subseteq \Rels$ be sets of relations,
   and let $\infsys=\pair{\schema}{\dataset}$ and  $\infsys'=\pair{\schema}{\dataset'}$ be information systems,
   then $\infsys\xrightarrow[I]{R} \infsys'$ is an event if and only if:
   \begin{align}
      \triple{a}{r}{b}\in\triples_{\dataset}-\triples_{\dataset'}&\Rightarrow\ r\in R
   \label{eqn:eventUnchanged}\\
      \triple{a}{r}{b}\in\triples_{\dataset'}-\triples_{\dataset}&\Rightarrow\ r\in(R \cup I)
   \label{eqn:eventInsert}
   \end{align}
   % was:
   % \begin{align}
   %    \triples_{\dataset} - (\Triple{\Atoms}{(R \cup I)}{\Atoms}) &= \triples_{\dataset'} - (\Triple{\Atoms}{(R \cup I)}{\Atoms})
   % \label{eqn:eventUnchanged}\\
   %    \triples_{\dataset} - (\Triple{\Atoms}{R}{\Atoms}) &\subseteq \triples_{\dataset'} - (\Triple{\Atoms}{R}{\Atoms})
   % \label{eqn:eventInsert}
   % \end{align}
   We say that event $\infsys\xrightarrow[I]{R} \infsys'$ brings the system $\infsys$ to $\infsys'$ inserting pairs in relations from $I$ and deleting pairs in relations from $R$.
\end{definition}

   Equation~\ref{eqn:eventUnchanged} states that the triples of those for relations in $I$ or $R$ are the only ones to have changed, and equation~\ref{eqn:eventInsert} states that of the ones that are only in $I$, no triples were removed.
   %If $I$ or $R$ is the empty set, we omit it from the arrow, so $\infsys \xrightarrow{R} \infsys'$ is a notation for $\infsys \xrightarrow[\emptyset]{R} \infsys'$.
